BETTING AND BELIEF: PREDICTION MARKETS AND ATTRIBUTION OF CLIMATE CHANGE

### 2016-07-11 wsc_final_submit/prediction_market_wsc.tex
Updated references to be all capital for first letters in the titles. Updated the header to be correct list of proceedings editor names.

\noindent {\bf JOHN J. NAY} is a Ph.D. Candidate at the Vanderbilt University School of Engineering and a Research Fellow at Vanderbilt Law School's Program on Law \& Innovation. He develops machine learning and computer simulation approaches to forecast dynamic systems and improve law and policy. His research involves collaboration with lawyers, social scientists, environmental scientists, and engineers. His email address is \email{john.j.nay@gmail.com}, and website: \href{http://johnjnay.com/}{http://johnjnay.com/}.\\

>>>>

\noindent {\bf JOHN J. NAY} is a Ph.D. Candidate at the Vanderbilt University School of Engineering and a Research Fellow at Vanderbilt Law School's Program on Law \& Innovation. He develops computational approaches to forecasting dynamic systems and improving law and policy, e.g. \href{http://predictgov.com/}{predictgov.com}. His email address is \email{john.j.nay@gmail.com}, and website: \href{http://johnjnay.com/}{http://johnjnay.com/}.\\
